### 2024-08-25 draft-2/draft-2.tex
insufficient condition for position legality when the en passant target is not none

\vskip-0.5\parskip If the en passant target is {\it n}\ot3 for some {\it n},
there is a white pawn at index {\it n}\ot4. If the en passant target is
{\it n}\ot6 for some {\it n}, there is a black pawn at index {\it n}\ot5.

>>>>

\vskip-0.5\parskip If the en passant target is {\it n}\ot3 for some {\it n},
the side to move is black and there is a white pawn at index {\it n}\ot4 and at
{\it n}\ot2 and {\it n}\ot3 the board is empty. If the en passant target is
{\it n}\ot6 for some {\it n}, the side to move is white and there is a black
pawn at index {\it n}\ot5 and at {\it n}\ot6 and {\it n}\ot7 the board is empty.
